Age-related changes in plant growth and traits

### 2016-10-13 scripts/Flowering_parts_charts.Rmd
lots of work summarizing nutrient data
most of the way to calculating RA using N & P, but some mis-matches with tissue names

``` {r}
accessoryList <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryList.csv")
accessoryListShort <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShort.csv")
accessoryListShortest <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShortest.csv")
tissue_energy <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/tissue_energy.csv")
nectar <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nectar.csv")

@@

View(SummaryInvest)

>>>>

``` {r}
accessoryList <- read.csv("~/Reproductive_Allocation_Kuringgai/data/accessoryList.csv")
accessoryListShort <- read.csv("~/Reproductive_Allocation_Kuringgai/data/accessoryListShort.csv")
accessoryListShortest <- read.csv("~/Reproductive_Allocation_Kuringgai/data/accessoryListShortest.csv")
tissue_energy <- read.csv("~/Reproductive_Allocation_Kuringgai/data/tissue_energy.csv")
nectar <- read.csv("~/Reproductive_Allocation_Kuringgai/data/nectar.csv")

@@

View(SummaryInvest)
names(Invest2)
